### 2015-05-27 writing/SNLI paper/entailment_eval.tex
Bit more cleanup.
Comments from KST and Ignacio.

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{numbers are still dev.}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}.
The best edit distance algorithm tunes the the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system makes use of information from
  WordNet \cite{miller1995wordnet} and VerbOcean
  \cite{chklovski2004verbocean}, and makes use of features
  based on tree patterns and dependency tree skeletons
  \cite{wang2007recognizing}.
Unsurprisingly, the classification-based approach outperforms simple
  edit distance metrics, and performs quite well despite relatively
  little lexicalization.

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, SNLI's size allows approaches which make use of
  rich lexicalized features.
We implmement such a lexicalized classifier as a strong baseline 
  for the task.
Our classifier implements 6 features:
\begin{enumerate}
\setlength\itemsep{-0.25em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the SNLI dataset, including precision/recall for the
  \textit{entailed} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
\todo{fill in dev numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

@@

The word embeddings for all of the moedels are initialized the 300d reference GloVe vectors \cite{pennington2014glove} and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensianal phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

>>>>

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}.
The best edit distance algorithm tunes the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system makes use of information from
  WordNet \cite{miller1995wordnet} and VerbOcean
  \cite{chklovski2004verbocean}, and makes use of features
  based on tree patterns and dependency tree skeletons
  \cite{wang2007recognizing}.
Unsurprisingly, the classification-based approach outperforms simple
  edit distance metrics, and performs quite well despite relatively
  little lexicalization.

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, SNLI's size allows approaches which make use of
  rich lexicalized features.
We implement such a lexicalized classifier as a strong baseline 
  for the task.
Our classifier implements 6 features:
\begin{enumerate}
\setlength\itemsep{-0.25em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the SNLI dataset, including precision/recall for the
  \textit{entailed} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
\todo{Final numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

@@

The word embeddings for all of the moedels are initialized the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}
